\textls[-0]{\thetitle}

### 2022-11-11 agda-files.tex
Reorder.

All the definitions contained in these files are stated in
terms of a meta\-language supporting quotient inductive-inductive types
(QIITs)~\cite{nordvall2010inductive,altkap2016}.
QIITs support equality constructors, which facilitate the expression of
conversion rules (e.g., \ruleref{tmeq/sub/id}).
%
We note that the current formalization is not checked by Agda because
Agda does not support QIITs natively and Agda does not support equality reflection.
An effort to mechanize the formalization is underway, using Agda's
\lsti{REWRITE} pragma to replace the limited uses of equality reflection, 
and using axioms to postulate QIIT type following \cite{altkap2016}.

>>>>

All the definitions contained in these files are stated in
terms of a meta\-language supporting quotient inductive-inductive types
(QIITs)~\cite{nordvall2010inductive,altkap2016}.
QIITs support equality constructors, which facilitate the expression of
conversion rules (e.g., \ruleref{tmeq/sub/id}).
%
We note that the current formalization is not checked by Agda because
Agda does not support equality reflection and Agda does not support QIITs natively.
An effort to mechanize the formalization is underway, using Agda's
\lsti{REWRITE} pragma to replace the limited uses of equality reflection, 
and using axioms to postulate QIIT type following \cite{altkap2016}.
